---
output: github_document
---

## ASCI

#### *Marcus W. Beck (maintainer), marcusb@sccwrp.org, Susanna Theroux, susannat@sccwrp.org, Quynh-Thi Ho, qthi.ho@gmail.com, John Van Sickle*

[![Travis-CI Build Status](https://travis-ci.org/SCCWRP/ASCI.svg?branch=master)](https://travis-ci.org/SCCWRP/ASCI)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/SCCWRP/ASCI?branch=master&svg=true)](https://ci.appveyor.com/project/SCCWRP/ASCI)
[![DOI](https://zenodo.org/badge/106055957.svg)](https://zenodo.org/badge/latestdoi/106055957)

R package materials to calculate the Algal Stream Condition Index (ASCI) based on O/E and pMMI scores using diatom, soft-bodied algae, or a hybrid appproach.

### Installation

Install the package as follows:

```{r, eval = FALSE}
install.packages('devtools')
library(devtools)
install_github('SCCWRP/ASCI')
library(ASCI)
```

### Citation

Please cite the current release as follows:

Marcus W Beck, Susanna Theroux, Quynh-Thi Ho, John Van Sickle (2019, July 25). SCCWRP/ASCI: v1.0.0. Zenodo. http://doi.org/10.5281/zenodo.1008839

### Usage

The sample file `demo_algae_tax` is included to demonstrate the correct format for input data. It is a `data.frame` of taxonomic data in long format (one row per sample). See the help files for more information (e.g., `?demo_algae_tax`)


```{r, message = F, warning = F, echo = F}
devtools::load_all()
```
```{r}
demo_results <- ASCI(demo_algae_tax)
demo_results
```

The output can be accessed using the defined methods.
```{r}
.S4methods(class = 'asci')
show(demo_results)
scores(demo_results)
Supp1_mmi(demo_results)
```

<!-- Summary of ASCI peformance statewide: -->
<!-- ```{r} -->
<!-- perf(allscr) -->
<!-- ``` -->




