---
output: github_document
---

## ASCI

#### *Marcus W. Beck (maintainer), marcusb@sccwrp.org, Susanna Theroux, susannat@sccwrp.org, Quynh-Thi Ho, qthi.ho@gmail.com, John Van Sickle*

[![Travis-CI Build Status](https://travis-ci.org/SCCWRP/ASCI.svg?branch=master)](https://travis-ci.org/SCCWRP/ASCI)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/SCCWRP/ASCI?branch=master&svg=true)](https://ci.appveyor.com/project/SCCWRP/ASCI)
[![DOI](https://zenodo.org/badge/106055957.svg)](https://zenodo.org/badge/latestdoi/106055957)

R package materials to calculate the Algal Stream Condition Index (ASCI) based on O/E and pMMI scores using diatom, soft-bodied algae, or a hybrid appproach.

### Installation

Install the package as follows:

```{r, eval = FALSE}
install.packages('devtools')
library(devtools)
install_github('SCCWRP/ASCI')
library(ASCI)
```

### Usage

The sample file `demo_algae_tax` is included to demonstrate the correct format for input data. It is a `data.frame` of taxonomic data in long format (one row per sample). See the help files for more information (e.g., `?demo_algae_tax`)

```{r, message = F, warning = F, echo = F}
devtools::load_all()
```
```{r}
head(demo_algae_tax)
```

The output is in a wide format.
```{r}
demo_results <- ASCI(demo_algae_tax)
demo_results
```




